My title

### 2024-11-24 paper/paper.qmd
fix some scripts & drew some more models

library(tidyverse)
library(arrow)
library(MASS)
library(GGally)
library(gridExtra)

data <- read_parquet(here::here("data/02-analysis_data/bodyfat.parquet"))
```

@@

@@

@@

# Histogram for Pct.BF
hist(data$Pct.BF, 
     main = "Histogram of Percent Body Fat",
     xlab = "Percent Body Fat",
     col = "lightblue",
     border = "black",
     breaks = 20)
```

@@

@@

@@

@@

>>>>

library(tidyverse)
library(arrow)
library(MASS)
library(GGally)
library(gridExtra)
library(knitr)
library(car)
library(kableExtra)

data <- read_parquet(here::here("data/02-analysis_data/bodyfat.parquet"))
raw_data <- read.table(here::here("data/01-raw_data/bodyfat.txt"))
```

@@

## Estimand

@@

cleaned data with normalized measurement 
```{r}
#| echo: false
#| warning: false
#| message: false

# Split into two smaller tables
part1 <- data[, 1:8]  # First 8 columns
part2 <- data[, 9:16]  # Remaining 8 columns

# Render each part
kable(head(part1, 10), booktabs = TRUE, caption = "Part 1: Columns 1-8") %>%
  kable_styling(latex_options = c("hold_position", "scale_down"))

kable(head(part2, 10), booktabs = TRUE, caption = "Part 2: Columns 9-16") %>%
  kable_styling(latex_options = c("hold_position", "scale_down"))
```

@@

# Histogram for Pct.BF
hist(data$Pct.BF, 
     main = "Histogram of Percent Body Fat",
     xlab = "Percent Body Fat",
     col = "#f88379",
     border = "black",
     breaks = 20)
```

@@

model <- lm(Pct.BF ~ Age + Height + Abdomen + Wrist, data = data)

# Calculate VIF
vif_values <- vif(model)

# Print VIF values
print(vif_values)
```

@@

# Fit the model
model <- lm(Pct.BF ~ Age + Height + Abdomen + Wrist, data = data)

# Extract coefficients, standard errors, and calculate 90% confidence intervals
coef_summary <- summary(model)$coefficients
conf_intervals <- confint(model, level = 0.90)  # 90% confidence intervals

# Create a data frame for plotting
coeff_data <- data.frame(
  Parameter = rownames(coef_summary),
  Estimate = coef_summary[, "Estimate"],
  Lower = conf_intervals[, 1],
  Upper = conf_intervals[, 2]
)

# Remove the intercept for better visualization (optional)
coeff_data <- coeff_data[coeff_data$Parameter != "(Intercept)", ]

# Create the plot
ggplot(coeff_data, aes(x = Estimate, y = Parameter)) +
  geom_point(size = 3, color = "#f88379") +
  geom_errorbarh(aes(xmin = Lower, xmax = Upper), height = 0.2,
                 color = "#f88379", linewidth = 0.8) +
  theme_minimal() +
  labs(
    title = "Model Coefficients",
    subtitle = "90% Confidence Intervals",
    x = "Coefficient Estimate",
    y = "Predictors"
  ) +
  theme(
    axis.title.y = element_text(size = 12, face = "bold"),
    axis.text.y = element_text(size = 10),
    plot.title = element_text(size = 14, face = "bold")
  )

```

@@

# Conclusion

@@

# Split into two smaller tables
part1 <- raw_data[, 1:8]  # First 8 columns
part2 <- raw_data[, 9:16]  # Remaining 8 columns

# Render each part
kable(head(part1, 10), booktabs = TRUE, caption = "Part 1: Columns 1-8") %>%
  kable_styling(latex_options = c("hold_position", "scale_down"))

kable(head(part2, 10), booktabs = TRUE, caption = "Part 2: Columns 9-16") %>%
  kable_styling(latex_options = c("hold_position", "scale_down"))
```
